# Введение {#intro}



1. После русских названий глав метка `{#label}` обязательна!

1. В `yaml` заголовок `index.Rmd` добавлено

```{yaml}
lang: ru-RU
otherlangs: en-GB
mainfont: "Linux Libertine O"
monofont: "Linux Libertine O"
sansfont: "Linux Libertine O"
```

1. В `_bookdown.yml` добавлено

```{yaml}
output_dir: docs
```

и `chapter_name` исправлено на "Глава "


1. Некоторые плагины Firefox могут блокировать рендеринг математических формул при публикации книжки на github.

Например, в Privacy Badger нужно разблокировать `mathjax.rstudio.com`. 


1. В `preamble.tex` добавлено:

```{yaml}
% why do we need \newfontfamily:
% http://tex.stackexchange.com/questions/91507/
\newfontfamily{\cyrillicfonttt}{Linux Libertine O}
\newfontfamily{\cyrillicfont}{Linux Libertine O}
\newfontfamily{\cyrillicfontsf}{Linux Libertine O}
```


Далее полезные хвосты из исходного примера:


```{r}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```






You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
